The K2 Bright Star Survey

### 2019-05-14 paper/ms.tex

% RGs, Classical pulsators 
\textcolor{red}{Variability catalog?}

>>>>

\subsection{Oscillating Red Giants}
\label{sec:rgs}
31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations. In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface. These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars.

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J} and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).

% RGs, Classical pulsators 
\subsection{Classical Variables}
\label{sec:variables}
\textcolor{red}{Variability catalog?}

\subsection{Chemically-Peculiar Stars}
